Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2024-12-17 paper/paper.tex
abstract

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Ensuring fairness in AI systems is crucial, but auditing these systems often requires sensitive data, which raises security and privacy concerns. To address this, we introduce a framework that utilizes differentially private synthetic data for fairness evaluations. This approach allows auditors to assess AI systems without exposing sensitive information. Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data. Our results ... (to be continued)
\end{abstract}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Auditing AI systems often requires sensitive data, raising security and privacy concerns. To address this, we proffer a framework that leverages differentially private synthetic data for fairness evaluations. This approach enables auditors to assess AI systems without exposing sensitive information. Through experiments on datasets like Adult, COMPAS, and Diabetes, we compare fairness metrics of synthetic and real data. Our results show that synthetic data accurately reflect the fairness properties of real data to a reasonable extent.
\end{abstract}
